---
title: "Game of Thrones Analysis"
output: 
  flexdashboard::flex_dashboard:
    theme:
      bg: "#101010"
      fg: "#EDE7DC" 
      primary: "#800020"
      base_font:
        google: Prompt
      code_font:
        google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

# Character Connections

## Column {data-width=1000 .tabset}

### Book 1

```{r}
CG1
```

### Book 2

```{r}
CG2
```

### Book 3

```{r}
CG3
```

### Book 4

```{r}
CG4
```

### Book 5

```{r}
CG5
```


# Views

## Column {data-width=1000 .tabset}

### Season Views

```{r}
fig
```

### Episode Views

```{r}
Ep_views
```

### 8th Season

```{r}
gots8
```


# Directors

## Column {data-width=1000 .tabset}

### All Directors

```{r}
all_dir
```

### Directors 10m

```{r}
six_dir
```

### Directors 10M

```{r}
six_dir_bar
```


# Ratings

## Column {data-width=1000 .tabset}

### IMDb vs Metacritic

```{r}
imdbmeta
```

# Actors

## Column {data-width=1000 .tabset}

### Star 1

```{r}
plstar1
```

### Star 2

```{r}
plstar2
```

### Star 3

```{r}
plstar3
```


# Authors

## Column {data-width=500}

### Authors1

```{r}
author1
```

## Column {data-width=500}

### Authors2

```{r}
author2
```

# Battles and Characters

## Column {data-width=1000 .tabset}

### Attacker Size

```{r}
attack
```

### Lannisters

```{r}
lannisters
```

### Characters

```{r}
charact_appear
```


